\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}

\usepackage{graphics}

\title{Homework 18}
\author{Austin Frownfelter \and Matthew Bialecki}
\date{February 23, 2018}


\begin{document}

\maketitle

\section{Problem 29}
\begin{quote}
Show BP$\cdot$NP $\subseteq$ NP/Poly
\end{quote}

Let L $\in$ BP$\cdot$NP

\medskip
$\exists$ PTM M that runs nondeterministically in poly time.  

$\forall x$ Probability(M(x) is wrong) $\leq$ 0.4

\medskip
Construct an M', which is a randomized reduction of L to 3SAT, for $n^2$ times and takes the majority.

$\forall x$ P(M'(x) is wrong) $\leq \frac1{4^n}$

The probability on all inputs x that M' is wrong = 

\-\hspace{20px}$\Sigma_{i=1}^{2^n} p(M'(x_i) wrong) \leq \frac{2^n}{4^n} < 1$

Therefore, $\exists$ random string such that M' is right on all inputs with that string as advice.

M' decides L. L is randomly reducible to 3SAT.  

3SAT can be trivially solved by a family of NP/Poly circuits as it is verified in polynomial time.  

Since L is reducible to 3SAT, L can be solved by a family of NP/Poly circuits.

Thus, L $\subseteq$ NP/Poly.  Therefore, BP$\cdot$NP $\subseteq$ NP/Poly.

\section{Problem 30}
\begin{quote}
Show BPL $\in$ P
\end{quote}

Let L be an arbitrary language in BPL

$\exists$ PTM M $\exists$ k such that 
\begin{enumerate}
\item M runs in space $\leq \log(|x|)$
\item $x\in L$ $\reflectbox{R}A$ $M(x,A)$ accepts
\item $x\notin L$ $\reflectbox{R}A$ $M(x,A)$ rejects
\end{enumerate}

m = the number of bits in A.


\medskip
Randomly marry pairs of inputs.  P(wrong in entire marriage) = P(wrong$)^2$


\medskip
$x\in L$ $\exists w $ $\forall A$ M(x,A) $\lor$ M(x,A$\oplus$w) accepts

$x\notin L$ $\forall w $ $\exists A$ M(x,A) $\land$ M(x,A$\oplus$w) rejects


\medskip
$x\in L$ wrong $(\frac1{4^n})^2$

$x\notin L$ wrong $\frac2{4^n}$


\medskip
$x\in L$: E[\# bad advice at k weddings] = $2^m*(\frac1{4^n})^{k+1}$ $< 1$ (i.e. there is some chance)

$2^m < 4^{n(k+1)}$

$m < n(k+1)$ $\rightarrow$ $k > \frac{m}{2n}-1$

$m < \log(n)$ $\rightarrow$ $k > \frac{\log(n)}{2n} < 1$

\medskip
$x\notin L$: E[\# bad advice at k weddings] $\leq \frac{k+1}{4^n}$

$\frac{\log(n)}{2n}*\frac1{4^n} < 1$

\medskip
$\exists$ TM N in P:
\begin{enumerate}[label=]
\item Runs the BPL machine
\item Returns the result
\end{enumerate}


\medskip
The probability N returns an incorrect result is P(wrong$)^{\log(n)}$

It is possible to drive P(wrong) from $\frac13$ to $\frac1{3^n}$ with the error reduction strategy in polynomial time.  Thus, the probability N is correct is effectively 100\%.  Therefore, N is in P.

N only uses log space, therefore it can be used to solve L in BPL, satisfying BPL.

Therefore, L $\in$ P

Therefore, BPL $\in$ P


\end{document}
























