\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}

\usepackage{graphics}

\title{Homework 19}
\author{Austin Frownfelter \and Matthew Bialecki}
\date{February 26, 2018}


\begin{document}

\maketitle

\section{Problem 29}
\begin{quote}
Show that if $\overline{3SAT} \leq _{r} 3SAT$ then PH collapses to $\Sigma_3^p$
\end{quote}

Informal proof:

Assume there is a randomized reduction from $\overline{3SAT}$ to 3SAT.  Then there exists a function which maps $\overline{3SAT}$ to 3SAT with some probability of correctness $\geq \frac23$.

To make this a certain function (with probability = 1), expand the function to a $\Sigma_3^p$ function.

This function must take $\Sigma_3^p$ or harder to decide.  Therefore, it is $\Sigma_3^p$-complete.

This $\Sigma_3^p$ function is closed under its complement.  Therefore, $\Sigma_3^p$ = $\Pi_3^p$.  Therefore, PH collapses to $\Sigma_3^p$.

\noindent\rule{\linewidth}{1pt}

$L \in \overline{3SAT}$

$L \leq _r L'$

$L' \in $ 3SAT

Define a PTM M such that if $x\in L$ most advice A will cause M(x,A) to accept, and if $x\notin L$ most advice A will cause M(x,A) to reject.

\medskip
There exists a TM N:
\begin{enumerate}[label=]
\item $x\in L$: $ \forall a\exists w\forall A N(x,a,w,A)$ accepts
\item $x\notin L$: $ \exists a\forall w\exists A N(x,a,w,A)$ rejects
\end{enumerate}

For $\overline{3SAT}$, N(x,a,w,A) runs M(x,A), M(x,a), M(x,a$\oplus w_1$), ..., M(x,a$\oplus w_k$) and accepts if 1 of them accepts and rejects if all reject.

For $3SAT$, N(x,a,w,A) runs M(x,A), M(x,a), M(x,a$\oplus w_1$), ..., M(x,a$\oplus w_k$) and accepts if all reject and rejects if 1 of them accepts.

This shows if there exists a randomized reduction from $\overline{3SAT}$ to 3SAT, then the resulting language is $\Sigma_3^p$-complete.  Also, it is closed under its complement (the complement is the negation of the quantifiers.) Thus it is also $\Pi_3^p$-complete.  Therefore, the Polynomial Hierarchy would collapse down to $\Sigma_3^p$.

\end{document}
























